Low Complexity Adaptive Sonar Imaging

### 2016-03-02 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2016:03:02	14:55:20	(on. 2.mars)

The output $z[n]$ of a beamformer is defined as the weighted sum of all the delayed data samples:
%
\begin{align}
z[n] = \w\H[n]\x[n] = \bmat{w_0[n]\\w_1[n]\\\vdots\\w_{M-1}[n]}^H \bmat{x_0[n]\\x_1[n]\\\vdots\\x_{M-1}[n]},\label{eq:beamformer_output}
\end{align}
%
where $w_m$ is the weight factor assigned to channel $m$. A weight set is commonly called a window, apodization or taper function. If the window real its response is symmetric. Applying a real window that trails off towards the edges creates a response with lower sidelobe levels and wider mainlobe, which translates into improved noise suppression at the cost of reduced resolution, respectively~\cite{Harris1978}.

@@

Since pixels are correlated laterally, we can include a weighted combination of these as well to improve the variance estimation:
%
\begin{align}
s_z^2 = \frac{1}{N_x N_k} \sumb{\nmat{\scriptstyle x'=\\[-2mm]\scriptstyle x-X}}{x+X} \sumb{\nmat{\scriptstyle n'=\\[-2mm]\scriptstyle n-K}}{n+K} \omega[x',n']\big| z[x',n'] \big|^2
\end{align}
%
where $N_x = 2X+1$ is the number of azimuth lines to average over, and $\omega[x',n']$ is a normalized 2 dimensional weight function. However, we observed no visual improvement doing this, and the effect of phase-steered windows is hard to predict. Henceforth no lateral averaging will be applied.
% 
% \begin{itemize}
% \item \emph{Window function}
% \item \emph{Parameter boundaries}
% \item \emph{Number of windows needed}
% \item \emph{Oversampling need}
% \item \emph{Image quality}
% \end{itemize}

>>>>

The output $z[n]$ of a beamformer is defined as the weighted sum of all the delayed data samples:
%
\begin{align}
z[n] = \w\H[n]\x[n] = \bmat{w_0[n]\\w_1[n]\\\vdots\\w_{M-1}[n]}^H \bmat{x_0[n]\\x_1[n]\\\vdots\\x_{M-1}[n]},\label{eq:beamformer_output}
\end{align}
%
where $w_m$ is the weight factor assigned to channel $m$. A weight set is commonly called a window, apodization or taper function. When the window is real its response is symmetric. Applying a real window that trails off towards the edges creates a response with lower sidelobe levels and wider mainlobe, which translates into improved noise suppression at the cost of reduced resolution, respectively~\cite{Harris1978}.

@@

If the pixels are correlated laterally, we can include a weighted combination of these as well to improve the variance estimation:
%
\begin{align}
s_z^2 = \frac{1}{N_x N_k} \sumb{\nmat{\scriptstyle x'=\\[-2mm]\scriptstyle x-X}}{x+X} \sumb{\nmat{\scriptstyle n'=\\[-2mm]\scriptstyle n-K}}{n+K} \omega[x',n']\big| z[x',n'] \big|^2
\end{align}
%
where $N_x = 2X+1$ is the number of azimuth lines to average over, and $\omega[x',n']$ is a normalized 2 dimensional weight function. Since we oversample slightly laterally when we delay each pixel (see Section \ref{sec:lca_oversampling}), we thought the lateral correlation to be sufficient to benefit from this. However, we observed no visual improvement applying this averaging in our case. Also, since the effect of phase-steering windows is hard to predict. Henceforth no lateral averaging will be applied.
% 
% \begin{itemize}
% \item \emph{Window function}
% \item \emph{Parameter boundaries}
% \item \emph{Number of windows needed}
% \item \emph{Oversampling need}
% \item \emph{Image quality}
% \end{itemize}
